---
title: "Simple document0915"
output:   
  html_document:
    toc: true
    toc_float: true
---

```{r, echo=FALSE,message=FALSE}
library(tidyverse)
```

I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r round(mean(samp),2)`.

# Section 3

This is going to make a plot! First U generate a dataframe, then use "ggplot" to make a scatterplot.

library(tidyverse)

# plot using ggplot 

```{r chunk_histogram}
plot_df = 
  tibble(
    x = rnorm(n = 1000),
    y = 1 +2 * x^2 + rnorm(n = 1000)
  )

ggplot(plot_df, aes(x = x)) + geom_histogram()

ggplot(plot_df, aes( x = x, y = y)) + geom_point()
```


Section 4
Write a named code chunk that creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. Then, produce a histogram of the absolute value variable just created. Add an inline summary giving the median value rounded to two decimal places. What happens if you set eval = FALSE to the code chunk? What about echo = FALSE?

Create a numeric variable containing a random sample of size 500 from a normal variable with mean 1
```{r}
la_df = 
  tibble(
    norm = rnorm(n = 500, mean = 1),
    logical = norm>0,
    abs_norm = abs(norm),
    round(median(norm),2)
)

ggplot(la_df, aes(x = abs_norm)) + geom_histogram()
```


* Key points
  * Formatting

Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell


```{r}

```














